Schema Change: Challenge Problems

### 2024-05-23 paper.tex
Add unification notes and diagrams
arrow diagrams

\usepackage{csquotes}
\usepackage{changepage}
\usepackage{multicol}
\usepackage{ccicons}
\usepackage[many]{tcolorbox}
\lstdefinelanguage[programming]{TeX}[AlLaTeX]{TeX}{%
  deletetexcs={title,author,bibliography},%
  deletekeywords={tabular},
  morekeywords={abstract},%
  moretexcs={chapter},%
  moretexcs=[2]{title,author,subtitle,keywords,maketitle,titlerunning,authorinfo,affiliation,authorrunning,paperdetails,acks,email},
  moretexcs=[3]{addbibresource,printbibliography,bibliography},%
}%
\lstset{%
  language={[programming]TeX},%
  keywordstyle=\firamedium,
  stringstyle=\color{RosyBrown},%
  texcsstyle=*{\color{Purple}\mdseries},%
  texcsstyle=*[2]{\color{Blue1}},%
  texcsstyle=*[3]{\color{ForestGreen}},%
  commentstyle={\color{FireBrick}},%
  escapechar=`,}
\newcommand*{\CTAN}[1]{\href{http://ctan.org/tex-archive/#1}{\nolinkurl{CTAN:#1}}}
%%

@@

@@

>>>>

\usepackage{csquotes}
\usepackage{changepage}
\usepackage{multicol}
\usepackage{ccicons}
\usepackage[many]{tcolorbox}
\usepackage{tikz-cd}

\lstdefinelanguage[programming]{TeX}[AlLaTeX]{TeX}{%
  deletetexcs={title,author,bibliography},%
  deletekeywords={tabular},
  morekeywords={abstract},%
  moretexcs={chapter},%
  moretexcs=[2]{title,author,subtitle,keywords,maketitle,titlerunning,authorinfo,affiliation,authorrunning,paperdetails,acks,email},
  moretexcs=[3]{addbibresource,printbibliography,bibliography},%
}%
\lstset{%
  language={[programming]TeX},%
  keywordstyle=\firamedium,
  stringstyle=\color{RosyBrown},%
  texcsstyle=*{\color{Purple}\mdseries},%
  texcsstyle=*[2]{\color{Blue1}},%
  texcsstyle=*[3]{\color{ForestGreen}},%
  commentstyle={\color{FireBrick}},%
  escapechar=`,}
\newcommand*{\CTAN}[1]{\href{http://ctan.org/tex-archive/#1}{\nolinkurl{CTAN:#1}}}
%%

@@

% UNIFIED VERSION
%
% 1. past improvements & feedback loops
% 2. for this we need to transcend treating state as ephemeral and adopt systems view
% 3. two current directions - live and collaborative
% 4. we welcome this development, but it poses challenges for programming systems
% 5. schema change in databases, hot reloading in programming, dynamic software update
% (maybe) pace layers and structure
% 6. contributions are a (i) framework and (ii) challenges

@@

\section{diagrams}

\begin{figure}

  \begin{tikzcd}[sep = huge]
    schema_1  \arrow[r, "constrains"] \arrow[d, "change"{left},""{name=L}]& data_1 \arrow[d, ""{name=R, left}, "migration"{right}] \\
    schema_2 \arrow[r, "constrains"{below}] & data_2
    \arrow[Rightarrow, from=L, to=R, "propagate"]
  \end{tikzcd}

  \begin{tikzcd}[sep = huge]
    schema_1  \arrow[r, "constrains"] \arrow[d, "change"{left},""{name=L}]& code_1 \arrow[d, ""{name=R, left}, "refactor"{right}] \\
    schema_2 \arrow[r, "constrains"{below}] & code_2
    \arrow[Rightarrow, from=L, to=R, "propagate"]
  \end{tikzcd}

  \caption{Commutative diagrams.}
  \label{fig:diagrams}
\end{figure}
